### 2020-06-02 writeup/setup.tex
add overview

\textbf{Proof Overview.}
The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
The result for more than two tasks is deferred to Appendix \ref{app_proof_many_tasks}.

>>>>

\textbf{Proof Overview.} The proof of Theorem \ref{lem_cov_shift_informal} uses the Stieltjes transform method (or the resolvent method) in random matrix theory \cite{bai2009spectral,tao2012topics,erdos2017dynamical}. Roughly speaking, we study the resolvent $R(z):=[\Sigma_2^{-1/2}( X_1^{\top}X_1 + X_2^{\top}X_2)\Sigma_2^{-1/2}-z]^{-1}$ for $z\in \C$ around $z=0$. Using the methods in \cite{Anisotropic,yang2019spiked}, we find the asymptotic limit, say $R_\infty(z)$, of $R(z)$ for any $z$ as $p\to \infty$ with an almost optimal convergence rate. In particular, when $z=0$, $\tr R_\infty(0)$ gives the right hand side of \eqref{eq_introX1X2}, which concludes Theorem \ref{lem_cov_shift_informal}. The details can be found in Appendix \ref{sec_maintools}-\ref{sec_Gauss}.

With  Theorem \ref{lem_cov_shift_informal}, we can calculate $\te(\hat{\beta}_t^{\MTL})$ and the term in \eqref{eq_te_var}, and their differences are given approximately by $\Delta_{\vari}$. On the other hand, the derivative of $R(z)$ with respect to $z$ can be approximated by $R_\infty'(z)$, which will be used to estimate the first term on the right hand side of \eqref{eq_te_model_shift}. During this process, we will get the $\Delta_{\bias}$ term up to an error $\delta$ depending on $\rho_1$. All these estimates combined give Theorem \ref{thm_main_informal}, and the details are presented in Appendix \ref{app_proof_main}.

%The proof of Theorem \ref{thm_main_informal} is presented in Appendix \ref{app_proof_main}.
We have a similar theorem for more than two tasks but with the matrix $X_i=X$, and it is deferred to Appendix \ref{app_proof_many_tasks}.
